### 2016-01-22 00-abstract.tex
Polish on 01. Add 06.
Abstract edit: point out overlapping community detection != clustering

Recent advancements in machine learning algorithms have transformed the data
analytics domain and provided innovative solutions to inherently difficult
problems. However, training models at scale over large data sets remains a
daunting challenge. One such problem is the detection of overlapping
communities within graphs. For example, a social network can be modeled as a
graph where the vertices and edges represent individuals and their
relationships. In this paper, we present and evaluate an efficient parallel and
distributed implementation of a Stochastic Gradient Markov Chain Monte Carlo
algorithm that solves the overlapping community detection problem. We show that
the algorithm can scale and process graphs consisting of billions of edges and
tens of millions of vertices on a compute cluster of 65 nodes.

>>>>

Recent advancements in machine learning algorithms have transformed the data
analytics domain and provided innovative solutions to inherently difficult
problems. However, training models at scale over large data sets remains a
daunting challenge. One such problem is the detection of overlapping
communities within graphs. For example, a social network can be modeled as a
graph where the vertices and edges represent individuals and their
relationships. As opposed to the problem graph partitioning or clustering, an
individual can be part of multiple communities which significantly increases
the problem complexity.
In this paper, we present and evaluate an efficient parallel and
distributed implementation of a Stochastic Gradient Markov Chain Monte Carlo
algorithm that solves the overlapping community detection problem. We show that
the algorithm can scale and process graphs consisting of billions of edges and
tens of millions of vertices on a compute cluster of 65 nodes. To the best of
our knowledge, this is the first time that the problem of deducing overlapping
communities has been learned for problems of such a large scale.
